Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-12 examples.tex

In Figure \ref{fig:mapping_code}, we see

@@

\subsection{Unmapping a Page}
The reverse operation, unmapping a designated page that is currently mapped, is pleasingly the reverse: by flipping the entry back to an invalid entry, full ownership of the updated entry reverts back to the now-invalid cell of the L1 table.

>>>>

In Figure \ref{fig:mapping_code}, we see an address ($\vaddr$) currently not mapped to a page ($\theta \; !!\; \vaddr = \texttt{None}$). The assurance of L1 table entry is provided by a page-worth \textit{virtual-pointsto} from an address (\texttt{pte\_addr}) stored in \textsf{rax} register (Specline 7) together with the assurance on the existence of L4, L3, and L2 table lookups (Speclines 4-6).

@@

\subsection{Unmapping a Page}
The reverse operation, unmapping a designated page that is currently mapped, is pleasingly the reverse: by flipping the entry back to an invalid entry, full ownership of the updated entry reverts back to the now-invalid cell of the L1 table.
